JD notes on effects

### 2022-08-26 manuscript/body.tex
Additional slides

Representative values for a focal predictor are generally chosen using quantiles, or equally spaced values, for a continuous predictor; or an exhaustive set of levels for a categorical predictor.
The central estimates are then calculated by holding the non-focal predictors at a reference point (a value chosen for a non-focal predictor) while varying the focal predictor, with the goal that the estimates represent how the model responds to the changes in the focal predictor \citep{fox2009effect, hanmer2013behind}. These values have been called: \emph{predictor effects} \citep{fox2009effect}, \emph{marginal predictions} \citep{leeper2017package} or \emph{estimated marginal means} \citep{lenth2018package} In this article, we refer to these quantities as the \emph{central estimates} of the outcome.

@@

\item [Model center] Is the value of the central estimate calculated using focal and non-focal model center values. It is a calculation that is equal to the average of central estimates for a linear model (identity link function) without complex interactions. The average of the linear predictor variables corresponding to the focal non-focal predictors are the focal and non-focal model center. Focal and non-focal model center values is also referred to as \emph{center point}. For simple continuous input variables, averaging linear predictor variables is the same as averaging the input variables (see \FREF{justify_plots}).

>>>>

Representative values for a focal predictor are generally chosen using quantiles, or equally spaced values, for a continuous predictor; or an exhaustive set of levels for a categorical predictor.
The central estimates are then calculated by holding the non-focal predictors at a reference point (a value chosen for a non-focal predictor) while varying the focal predictor, with the goal that the estimates represent how the model responds to the changes in the focal predictor \citep{fox2009effect, hanmer2013behind}. These values have been called: \emph{predictor effects} \citep{fox2009effect}, \emph{marginal predictions} \citep{leeper2017package} or \emph{estimated marginal means} \citep{lenth2018package}. In this article, we refer to these quantities as the \emph{central estimates} of the outcome.

@@

\item [Model center] Is the value of the central estimate calculated using focal and non-focal model center values. It is a calculation that is equal to the average of central estimates for a linear model (identity link function) without complex interactions. The average of the linear predictor variables corresponding to the focal and non-focal predictors are the focal and non-focal model center, respectively. Focal and non-focal model center values are also referred to as \emph{center point}. For simple continuous input variables, averaging linear predictor variables is the same as averaging the input variables (see \FREF{justify_plots}).
